|

### 2020-03-24 inst/manuscript/candidaev_supplement.Rmd
Update affiliation in supplementary
Also, fix typo in Table S2.

---
title: | 
   **Supplement to: Protein markers for *Candida albicans* EVs include
   claudin-like Sur7 family proteins**
author: | 
   | Charlotte Dawson^a^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
     Pierre Faou^b^,
   | Mark Bleackley^a^, Marilyn Anderson^a^
date: | 
   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
     Molecular Science, La Trobe University, 
     Melbourne, 3086, Victoria, Australia*
   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
     Molecular Science, La Trobe University, Melbourne, 
     3086, Victoria, Australia*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/taylor-and-francis-acs.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \newcommand{\beginsupplement}{
      \setcounter{table}{0} 
      \renewcommand{\thetable}{S\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{S\arabic{figure}}
    }
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

@@

fs3b <- nta_total %>% 
  ggboxplot(x = "strain", y = "Particle_count", 
            color = "strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15, 
            ylab = "Total particle concentration / mL") + 
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1e13)) + 
  theme(axis.title.x = element_blank(), 
        legend.position = "none") + 
  stat_compare_means(method = "kruskal.test", 
                     label.x = 0.82, 
                     label.y = 9.7e12) +
  stat_pvalue_manual(conc_dunns[c(2), ], label = "p.adj", 
                     y.position = 8.8e12) + 
  coord_cartesian(clip = "off")

@@

# Fig S4B = compare compare enrichment of common proteins to DAYY286 yeast EVs
# and DAY286 biofilm EVs via volcano plot
fS4_b <- plot_volcano(data = ev_res, 
                        p_val = adj.P.Val, 
                        log2fc = logFC,
                        group = group, 
                        use_labels = TRUE,
                        label_fun = ifelse(logFC >= 5 | logFC <= -5, 
                                           CGD_gene_name, ""), 
                        point_size = 0.6, 
                        label_size = 2, 
                        x_lim = c(-8, 8), 
                        y_lim = c(0, 8), 
                        legend_params = c("left", 11, 8), 
                        axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("Yeast EV enriched", 
                                 "Biofilm EV enriched", 
                                 "Not significant"), 
                      values = c("#0072B2", 
                                 "#999999", 
                                 "#D55E00"), 
                      breaks = c("Y_EV up", "B_EV up", "not sig"), 
                      name = element_blank()) + 
  annotate("text", x = 5.5, y = 0.5, label = "bold('DAY286')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('136')", 
           parse = TRUE, colour = "#D55E00") + 
  annotate("text", x = -3.5, y = 7, label = "bold('129')", parse = TRUE, 
           colour = "#0072B2") + 
  annotate("text", x = 0, y = 6, label = "bold('168')", parse = TRUE, 
           colour = "#999999") + 
  theme(legend.position = "right")

>>>>

---
title: | 
   **Supplement to: Protein markers for *Candida albicans* EVs include
   claudin-like Sur7 family proteins**
author: | 
   | Charlotte Dawson^ac^, Donovan Garcia Ceron^a^, Harinda Rajapaksha^b^, 
     Pierre Faou^b^,
   | Mark Bleackley^a^, Marilyn Anderson^a^
date: | 
   | *^a^Department of Biochemistry and Genetics, La Trobe Institute for 
     Molecular Science, La Trobe University, 
     Melbourne, 3086, Victoria, Australia*
   | *^b^La Trobe Comprehensive Proteomics Platform, La Trobe Institute for 
     Molecular Science, La Trobe University, Melbourne, 
     3086, Victoria, Australia*
   | *^c^Cambridge Centre for Proteomics, Milner Therapeutics Institute, 
     Jeffrey Cheah Biomedical Centre, University of Cambridge, 
     Puddicombe Way, Cambridge CB2 0AW, United Kingdom*
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
      fig_caption: yes
      number_sections: yes
      toc: no
      keep_tex: no
bibliography: "components/references.bib" 
csl: "components/taylor-and-francis-acs.csl"
link-citations: yes
linkcolor: black
fontsize: 12pt
geometry: margin=1in
classoption: letterpaper
mainfont: Times New Roman
linestretch: 1.5
header-includes:
  - \usepackage{titling}
  - \pretitle{\begin{center}\fontsize{14bp}{14bp}\selectfont}
  - \posttitle{\par\end{center}}
  - \preauthor{\begin{center}\fontsize{12bp}{12bp}\selectfont}
  - \postauthor{\par\end{center}}
  - \predate{\begin{center}\fontsize{10bp}{10bp}\selectfont}
  - \postdate{\par\end{center}}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \setlength{\headheight}{15pt}
  - \usepackage{float}
  - \let\origfigure\figure
  - \let\endorigfigure\endfigure
  - \renewenvironment{figure}[1][2]{\expandafter\origfigure\expandafter[H]}
    {\endorigfigure}
  - \newcommand{\beginsupplement}{
      \setcounter{table}{0} 
      \renewcommand{\thetable}{S\arabic{table}} 
      \setcounter{figure}{0} 
      \renewcommand{\thefigure}{S\arabic{figure}}
    }
  - \usepackage{caption}
  - \captionsetup{font={normalsize,stretch=1.3},labelfont=bf}
  - \usepackage{threeparttable}
---

@@

fs3b <- nta_total %>% 
  ggboxplot(x = "strain", y = "Particle_count", 
            color = "strain", palette = st_pal, add = "jitter", 
            add.params = list(color = "black"), 
            shape = 15, 
            ylab = "Total particle concentration / mL", 
            outlier.shape = NA) + 
  scale_y_continuous(expand = c(0, 0), 
                     limits = c(0, 1e13)) + 
  theme(axis.title.x = element_blank(), 
        legend.position = "none") + 
  stat_compare_means(method = "kruskal.test", 
                     label.x = 0.82, 
                     label.y = 9.7e12) +
  stat_pvalue_manual(conc_dunns[c(2), ], label = "p.adj", 
                     y.position = 8.8e12) + 
  coord_cartesian(clip = "off")

@@

# Fig S4B = compare compare enrichment of common proteins to DAYY286 yeast EVs
# and DAY286 biofilm EVs via volcano plot
fS4_b <- plot_volcano(data = ev_res, 
                        p_val = adj.P.Val, 
                        log2fc = logFC,
                        group = group, 
                        use_labels = TRUE,
                        label_fun = ifelse(logFC >= 5 | logFC <= -5, 
                                           CGD_gene_name, ""), 
                        point_size = 0.6, 
                        label_size = 2, 
                        x_lim = c(-8, 8), 
                        y_lim = c(0, 8), 
                        legend_params = c("left", 11, 8), 
                        axis_params = c("black", 10)) + 
  scale_colour_manual(labels = c("Yeast EV enriched", 
                                 "Biofilm EV enriched", 
                                 "Not significant"), 
                      values = c("#D55E00", 
                                 "#0072B2", 
                                 "#999999"), 
                      breaks = c("Y_EV up", "B_EV up", "not sig"), 
                      name = element_blank()) + 
  annotate("text", x = 5.5, y = 0.5, label = "bold('DAY286')", parse = TRUE) + 
  annotate("text", x = 3.5, y = 7, label = "bold('136')", 
           parse = TRUE, colour = "#D55E00") + 
  annotate("text", x = -3.5, y = 7, label = "bold('129')", parse = TRUE, 
           colour = "#0072B2") + 
  annotate("text", x = 0, y = 6, label = "bold('168')", parse = TRUE, 
           colour = "#999999") + 
  theme(legend.position = "right")
